Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-17 paper.tex
Minor correction
Change acknowledgement so that it's clear that only OSRA was dunded by NIH

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
  \ifthenelse{\boolean{publ}}{\small}{}
  NMOB is supported by a Health Research Board Career Development
Fellowship (PD/2009/13).
This project has been funded in whole or in part with federal funds from
the National Cancer Institute, National Institutes of Health, under
contract HHSN261200800001E. The content of this publication does not
necessarily reflect the views of the policies of the Department of
Health and Human Services, nor does mention of trade names, commercial
products, or organisations imply endorsement by the US Government.

@@

  \subsection*{Table 2 - Open Data in chemistry.}
    Overview of major open chemical data available under a license or waiver
    compatible with the Panton Principles.
    \par \mbox{}
    \par
    \mbox{
\begin{tabular}{|l|c|l|}
  %% \hline \multicolumn{3}{|c|}{My Table}\\ \hline
  \hline \textbf{Name} & \textbf{License/Waiver} & \textbf{Description} \\ \hline
  \textbf{ChemPedia} & CC0 & Crowd-sourced chemical names (project discontinued) \\ \hline
  \textbf{CrystalEye}     & PPDL & Crystal structures from primary literature \\ \hline
  \textbf{ONS Solubility} & CC0 & Solubility data for various solvents \\ \hline
  \textbf{Reaction Attempts} & CC0 & Data on successful and unsuccessful reactions \\ \hline
\end{tabular}
      }

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
  \ifthenelse{\boolean{publ}}{\small}{}
  NMOB is supported by a Health Research Board Career Development
Fellowship (PD/2009/13).
The OSRA project has been funded in whole or in part with federal funds from
the National Cancer Institute, National Institutes of Health, under
contract HHSN261200800001E. The content of this publication does not
necessarily reflect the views of the policies of the Department of
Health and Human Services, nor does mention of trade names, commercial
products, or organisations imply endorsement by the US Government.

@@

  \subsection*{Table 2 - Open Data in chemistry.}
    Overview of major open chemical data available under a license or waiver
    compatible with the Panton Principles.
    \par \mbox{}
    \par
    \mbox{
\begin{tabular}{|l|c|l|}
  %% \hline \multicolumn{3}{|c|}{My Table}\\ \hline
  \hline \textbf{Name} & \textbf{License/Waiver} & \textbf{Description} \\ \hline
  \textbf{Chempedia} & CC0 & Crowd-sourced chemical names (project discontinued) \\ \hline
  \textbf{CrystalEye}     & PPDL & Crystal structures from primary literature \\ \hline
  \textbf{ONS Solubility} & CC0 & Solubility data for various solvents \\ \hline
  \textbf{Reaction Attempts} & CC0 & Data on successful and unsuccessful reactions \\ \hline
\end{tabular}
      }
